\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/triggers.tex
fix bad ref

To create an SBO-triggered payload program, we make the following code pattern,
as seen from Kiriansky and Waldspurger's Spectre~1.1
description~\cite{kiransky2018speculative}:
\begin{lstlisting}
    if (y < lenc)
        c[y] = z;
\end{lstlisting}
With user controlled 
\texttt{y} and \texttt{z} and sporadically uncached \texttt{lenc}, an attacker 
can \textit{speculatively} overflow array \texttt{c}
to overwrite a return address (or function pointer, etc) and redirect control
flow. Note that the bounds check on \texttt{y} will ensure that this program
will not actually allow a buffer overflow to occur, but the attacker can
nonetheless use this to influence a speculative entry point based on their
choice of \texttt{y} and \texttt{z}.

>>>>

To create an SBO-triggered payload program, we make the following code pattern,
as seen from Kiriansky and Waldspurger's Spectre~1.1
description~\cite{kiriansky2018speculative}:
\begin{lstlisting}
    if (y < lenc)
        c[y] = z;
\end{lstlisting}
With user controlled 
\texttt{y} and \texttt{z} and sporadically uncached \texttt{lenc}, an attacker 
can \textit{speculatively} overflow array \texttt{c}
to overwrite a return address (or function pointer, etc) and redirect control
flow. Note that the bounds check on \texttt{y} will ensure that this program
will not actually allow a buffer overflow to occur, but the attacker can
nonetheless use this to influence a speculative entry point based on their
choice of \texttt{y} and \texttt{z}.
